First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-02-02 eg6-letters/coherent/dvcs_he4_prl.tex
CLeaning the reference list, added the CFF formulas, and some minor fixings

A wealth of information on the quantum chromodynamics (QCD) lies in the 
internal structure of hadrons. In the recent past, the development of the 
generalized parton distributions (GPDs) framework has offered the possibility
to obtain new information about the momentum and spatial degrees of 
freedom of the quark and gluons inside hadrons 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.
In impact parameter space, the GPDs are indeed interpreted as a tomography of the 
transverse plane for partons carrying a certain longitudinal momentum 
\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep}.

The main access to GPDs is through the measurement of deep virtual Compton 
scattering (DVCS), i.e. the hard exclusive electroproduction of a real photon. 
While other processes are known to be sensitive to GPDs, the measurement of the
DVCS is considered as the cleanest probe and has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
[Should we cite less publications on the topic or a review?]
involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
CERN. The vast majority of these measurements was focused on the study of the 
proton structure and allow the extraction of the tomography of the nucleon,
for details on the formalism see 
\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}.
This framework is also applicable to nuclei, giving access to completely new 
information about the nuclear structure in terms of quarks and 
gluons \cite{Dupre:2015jha}.
The study of the 3D structure of the nuclei appears to be especially important
in light of the large nuclear effects observed in nuclear parton distribution 
functions \cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.

@@

Experimentally, the coherent nuclear DVCS channel is difficult to measure because of 
its small cross section and the necessity to ensure that the target remains 
intact while emitting a hard photon ($eA \rightarrow e' A' \gamma$). Figure 
\ref{fig:diags} illustrates the hand bag diagram for the coherent DVCS on 
$^4$He. Similarly to the proton case, at large photon's 4-momentum square 
$Q^2$ ($= -(k-k')^{2}$) and small squared momentum transfer $t$ 
($= (p-p')^{2}$), the DVCS handbag diagram can be factorized into two parts 
\cite{Freund_Collins,Ji_Osborne}. The hard part includes photons-quark 
interaction and is calculable with perturbative QED, while the non-perturbative 
part is parametrized in terms of GPDs, which embed the partonic structure of 
the hadron. The GPDs depend on three variables $x$, $\xi$ and $t$, which are 
indicated in Figure \ref{fig:diags} for the DVCS process. In DVCS, $\xi$ can 
be related to the Bjorken variable $x_{B}$: $\xi\approx {{x_B}\over{2-x_B}}$, 
where $x_B=\frac{Q^2}{2M\nu}$ with $M$ the proton mass and 
$\nu=E_e-E_{e^\prime}$. One can easily access $t$ as the squared momentum 
transfered to the target, however the $x$ variable cannot be experimentally 
accessed in a DVCS reaction. Hence, we measure only complex Compton Form 
Factors (CFF) [need reference] defined as: [add FORMULA for CFFs].

The main challenge to study nuclear DVCS is to ensure the exclusivity of the 
reaction. Until now, the only available data set of nuclear DVCS
was from the HERMES experiment \cite{Ellinghaus:2002zw}, where exclusivity is 
based on kinematic cuts on the measured scattered electron and real photon only. 
The measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and 
Xe) but has been critisized for mixing coherent and incoherent processes 
[ref]. In this regard, the direct detection of the low-energy recoil nuclei is the best way to
garanty that the nuclei is intact and that the reaction did not occur on a 
bound nucleon. The CEBAF Large Acceptance Spectrometer (CLAS) setting  in the
Hall-B of JLab being already optimized for DVCS measurments 
[refs], we built a dedicated radial time projection chamber (RTPC) for 
the detection of the recoiling low energy nuclei in order to complete this
experimental setting. The $^4$He nucleus is an ideal experimental target in
this regard as it is light enough to be detected in such a setting, while it
is subject to significant nuclear effects \cite{JSeely} and has rather high 
density. Using a helium target leads to another important advantage, the number of GPDs 
defined for a hadron depends on its spin. The structure of a spin zero nuclei, such as 
$^4He$, is parametrized by only one chiral even GPD ($H_{A}(x,\xi,t)$) at 
leading twist, while 4 GPDs arise in the nucleon case. That significantly
simplifies the interpretation of the data and allow a model independent
extraction of the $^4$He CFF ($\mathcal{H}_{A}$) that will be presented at the
end of this letter.

@@

The experiment E08-024 took place in the experimental Hall-B of Jefferson 
laboratory (JLab) in 2009 using the nearly 100\% duty factor longitudinally 
polarized electron beam (83$\%$ polarization) at its full energy of 6.064 
GeV. The data were collected over three months using a 6 atm gaseous $^4$He 
target placed in the center of CLAS. For DVCS experiments, the CLAS base line 
design \cite{CLAS_ref} is supplemented with an inner calorimeter (IC) and a
solenoid. The IC extends the photon detection acceptance of CLAS, which is 
originally from 15$^{\circ}$ to 45$^{\circ}$, to polar angle as low 
as 4$^{\circ}$. At these small angles the low-energy M\o{}ller 
electrons produced in the target form a very high rate background that is
suppressed by a 5 Tesla solenoid placed around the target.

Because the coherent DVCS cross section is peaked at low $-t$, the recoil 
$^4$He nuclei produced in DVCS have a low average momentum around 250 MeV/c.
The CLAS cannot detect such low energy $\alpha$ particles, so in order to 
ensure the exclusivity of the measurement, we 
built a small and light RTPC to complement CLAS. Figure~\ref{fig:RTPC} presents 
the design of this RTPC that is surrounding the 
$^4$He gaseous target and inside the solenoid magnet.
The detector was specifically calibrated for the detection of
$^4$He nuclei using elastic scattering produced with a 1.2~GeV electron beam.

@@

The main backgroud to the measurement of DVCS is the coherent $\pi^{0}$ 
production. Therefore, we remove events where a $\pi^{0}$ can be identified 
by invariant mass reconstruction of two photons.  To ensure that the 
interaction occurs at the partonic level and that the DVCS handbag diagram is 
applicable we select events with $Q^{2}>1~[GeV^{2}/c^{2}]$. The exclusivity of 
the events is obtained by applying a set of cuts on the following kinematic 
variables: the co-planarity angle ($\Delta \phi$), the missing energy, the 
missing mass squared, the missing transverse momentum, the missing mass 
squared of the $e'^4He'$ system and the angle ($\theta$) between the measured 
photon and the missing momentum of the $e'^4He'$ system. The most relevant of 
these cuts are presented in Figure~\ref{fig:kin-cuts}, these are 3$\sigma$ 
cuts except for the missing energy that appears to be too large and for which 
we reduced the cut window to [-0.45,0.5] GeV. After these requirements, we 
have about 3500 events left, Figure \ref{fig:kin-coverage} presents their
kinematic distributions in ($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$).

@@

To interpret the DVCS, one has to keep in mind that this reaction is 
indistinguishable from the Bethe-Heitler (BH) process, where the final photon 
is emitted either from the incoming or the outgoing leptons. At leading twist 
and leading order, the deeply virtual photon production cross section is 
composed of a BH, a DVCS, and an interference terms. The amplitudes of the 
three terms can be approximated as a finite sum of Fourier harmonics as shown 
for the nucleon in \cite{Belitsky:2001ns} and for the spinless targets in 
\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on these calculations, the 
beam-spin asymmetry ($A_{LU}$) can then be expressed as:
\small
\begin{equation}
\begin{split}
A_{LU}(\phi) =~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
 \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( 
\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
\label{eq:A_LU-coh}
\end{split}
\end{equation}
\normalsize
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the $^4$He CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$. 
$\phi$ is the azimuthal angle between the ($e$,$e'$) and 
($\gamma^{*}$,$^4$He$'$) planes. The $\alpha_{i}$'s are $\phi$-dependent 
kinematical factors that depend on the nuclear form factor ($F_{A}(t)$) and the 
independent variables $Q^2$, $x_{B}$ and $t$. These factors are expressed as:
\small
\begin{eqnarray}
   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
C_{++}(1) cos(\phi) \right)\\
\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2}
\end{eqnarray}
\normalsize
Where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$ is the $^4$He mass, 
$\mathcal{P}_1(\phi)$ and $\mathcal {P}_2(\phi)$ are the Bethe-Heitler
propagators. The factors: $c_{0,1,2}^{BH}$, $c_0^{DVCS}$, $c_{0,1}^{INT}$ and
$s_1^{INT}$ are the Fourier coefficients of the BH, $S{++}(1)$, $C_{++}(0)$, 
and $C_{++}(1)$ are the Fourier harmonics in the leptonic tensor. The 
explicit expressions of these terms can be found in \cite{Belitsky:2008bz}. 
We see that using the $\sin(\phi)$ and $\cos(\phi)$ contributions, it is 
possible to extract 
$\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ from the beam spin
asymmetry.

@@

We display in figure \ref{fig:CFF_HA} our extraction of the $^4$He CFF 
$\mathcal{H}_A$ together with theoretical calculations from two models 
labeled: convolution, and off-shell models. In the convolution 
model \cite{Vadim_priv}, the nucleus is assumed to be composed of 
non-relativistic non-interacting nucleons, and these nucleons interact 
independently with the probe. The convolution/dual model is based on nucleon GPDs from 
the dual parametrization \cite{Guzey:2006xi}, the convolution/VGG uses nucleon GPDs  
from the VGG model, which is based on the double distributions ansatz 
\cite{DD_model}. The Off-shell model \cite{GonzalezHernandez:2012jv} relies on 
impulse approximation and uses advanced spectral function of the 
nuclei that accounts for all configurations of the final nuclear system and the 
binding effects between the nucleons.
[These need to be renamed on the figure, it does not make sense to call differently
models that are identical. We should also request the projections from Vadim
model: hep-ph/0509158.]

@@

\bibitem{Burkardt:2000za} 
  M.~Burkardt,
  Phys.\ Rev.\ D {\bf 62}, 071503 (2000)
  Erratum: [Phys.\ Rev.\ D {\bf 66}, 119903 (2002)]

\bibitem{Diehl:2002he} 
  M.~Diehl,
  Eur.\ Phys.\ J.\ C {\bf 25}, 223 (2002)
  Erratum: [Eur.\ Phys.\ J.\ C {\bf 31}, 277 (2003)]

@@

\bibitem{Belitsky}
A.~V.~Belitsky and A.~V.~Radyushkin, 
Phys.\ Rept.\ vol. 418 (2005)

\bibitem{Guidal:2013rya}
M.~Guidal, H.~Moutarde and M.~Vanderhaeghen,
Rept.\ Prog.\ Phys.\  {\bf 76}, 066202 (2013)

\bibitem{CLAS_ref}
B.A. Mecking {\it et al.}, 
Nucl.\ Inst.\ and Meth.\ A 503, 513 (2003)

\bibitem{eg6_note}
M. Hattawy {\it et al.} (CLAS-EG6 Working Group), 
CLAS internal analysis note, 2016.

@@

>>>>

A wealth of information on the quantum chromodynamics (QCD) lies in the 
internal structure of hadrons. In the recent past, the development of the 
generalized parton distributions (GPDs) framework has offered the possibility
to obtain new information about the momentum and spatial degrees of 
freedom of the quark and gluons inside hadrons 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.
In impact parameter space, the GPDs are indeed interpreted as a tomography of the 
transverse plane for partons carrying a certain longitudinal momentum 
\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep,Burkardt:2005hp}.

The main access to GPDs is through the measurement of deep virtual Compton 
scattering (DVCS), i.e. the hard exclusive electroproduction of a real photon. 
While other processes are known to be sensitive to GPDs, the measurement of the
DVCS is considered as the cleanest probe and has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
[Should we cite less publications on the topic or a review?]
involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
CERN. The vast majority of these measurements was focused on the study of the 
proton structure and allow the extraction of the tomography of the nucleon,
for details on the formalism see 
\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}.
This framework is also applicable to nuclei, giving access to completely new 
information about the nuclear structure in terms of quarks and 
gluons \cite{Dupre:2015jha}.
The study of the 3D structure of the nuclei appears to be especially important
in light of the large nuclear effects observed in nuclear parton distribution 
functions \cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.

@@

Experimentally, the coherent nuclear DVCS channel is difficult to measure because of 
its small cross section and the necessity to ensure that the target remains 
intact while emitting a hard photon ($eA \rightarrow e' A' \gamma$). Figure 
\ref{fig:diags} illustrates the hand bag diagram for the coherent DVCS on 
$^4$He. Similarly to the proton case, at large photon's 4-momentum square 
$Q^2$ ($= -(k-k')^{2}$) and small squared momentum transfer $t$ 
($= (p-p')^{2}$), the DVCS handbag diagram can be factorized into two parts 
\cite{Freund_Collins,Ji_Osborne}. The hard part includes photons-quark 
interaction and is calculable with perturbative QED, while the non-perturbative 
part is parametrized in terms of GPDs, which embed the partonic structure of 
the hadron. The GPDs depend on three variables $x$, $\xi$ and $t$, which are 
indicated in Figure \ref{fig:diags} for the DVCS process. In DVCS, $\xi$ can 
be related to the Bjorken variable $x_{B}$: $\xi\approx {{x_B}\over{2-x_B}}$, 
where $x_B=\frac{Q^2}{2M\nu}$ with $M$ the proton mass and 
$\nu=E_e-E_{e^\prime}$. One can easily access $t$ as the squared momentum 
transferred to the target, however the $x$ variable cannot be experimentally 
accessed in a DVCS reaction. Hence, we measure only complex Compton Form 
Factors (CFF) \cite{Guidal:2013rya}. That is, for a GPD at a given ($x,\xi,t$), 
we can measure experimentally the real ($\mathcal{P} 
\int_{0}^{1}dx[GPD(x,\xi,t)-GPD(-x,\xi,t)] \, C^{+}(x,\xi)$, with $\mathcal{P}$ 
stands for the Cauchy principal value integral and $C^{+}(x,\xi)$ is a 
coefficient function ($=  \frac{1}{x-\xi} + \frac{1}{x+\xi}$)) and the 
imaginary $(GPD(\xi,\xi,t)-GPD(-\xi,\xi,t)$) parts of it's corresponding CFF.

The main challenge in exploring nuclear DVCS is to ensure the exclusivity of 
the reaction. Until now, the only available data set of nuclear DVCS
was from the HERMES experiment \cite{Ellinghaus:2002zw}, where exclusivity is 
based on kinematic cuts on the measured scattered electron and real photon only. 
The measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and 
Xe) but has been criticized for mixing coherent and incoherent processes 
\cite{HERMES_BSA}. In this regard, the direct detection of the low-energy 
recoil nuclei is the best way to guarantee that the nucleus is intact and that 
the reaction did not occur on a bound nucleon. The CEBAF Large Acceptance 
Spectrometer (CLAS) setting  in the Hall-B of JLab being already optimized for 
DVCS measurements 
\cite{Mecking:2003zu,Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}, 
we built a dedicated radial time projection chamber (RTPC) for the detection of 
the recoiling low energy nuclei in order to complete this experimental setting.  
The $^4$He nucleus is an ideal experimental target in this regard as it is 
light enough to be detected in such a setting, while it
is subject to significant nuclear effects \cite{JSeely} and has rather high 
density. Using a helium target leads to another important advantage, the number of GPDs 
defined for a hadron depends on its spin. The structure of a spin zero nuclei, such as 
$^4He$, is parametrized by only one chiral even GPD ($H_{A}(x,\xi,t)$) at 
leading twist, while 4 GPDs arise in the nucleon case. That significantly
simplifies the interpretation of the data and allow a model independent
extraction of the $^4$He CFF ($\mathcal{H}_{A}$) that will be presented at the
end of this letter.

@@

The experiment E08-024 took place in the experimental Hall-B of Jefferson 
laboratory (JLab) in 2009 using the nearly 100\% duty factor longitudinally 
polarized electron beam (83$\%$ polarization) at its full energy of 6.064 
GeV. The data were collected over three months using a 6 atm gaseous $^4$He 
target placed in the center of CLAS. For DVCS experiments, the CLAS base line 
design \cite{Mecking:2003zu} is supplemented with an inner calorimeter (IC) and 
a solenoid. The IC extends the photon detection acceptance of CLAS, which is 
originally from 15$^{\circ}$ to 45$^{\circ}$, to polar angle as low as 
4$^{\circ}$. At these small angles the low-energy M\o{}ller electrons produced 
in the target form a very high rate background that is
suppressed by a 5 Tesla solenoid placed around the target.

Because the coherent DVCS cross section is peaked at low $-t$, the recoil 
$^4$He nuclei produced in DVCS have a low average momentum ($p/q$) around 150 
MeV/c. The CLAS spectrometer cannot detect such low energy $\alpha$ particles, 
so in order to ensure the exclusivity of the measurement, we built a small and 
light RTPC to complement CLAS. Figure~\ref{fig:RTPC} presents the design of 
this RTPC that is surrounding the $^4$He gaseous target and inside the solenoid 
magnet. The detector was specifically calibrated for the detection of
$^4$He nuclei using elastic scattering produced with a 1.2~GeV electron beam.

@@

The main background to the measurement of DVCS is the coherent $\pi^{0}$ 
production. Therefore, we remove events where a $\pi^{0}$ can be identified by 
invariant mass reconstruction of two photons.  To ensure that the interaction 
occurs at the partonic level and that the DVCS handbag diagram is applicable we 
select events with $Q^{2}>1~[GeV^{2}/c^{2}]$. The exclusivity of the events is 
obtained by applying a set of cuts on the following kinematic variables: the 
co-planarity angle ($\Delta \phi$), the missing energy, the missing mass 
squared, the missing transverse momentum, the missing mass squared of the 
$e'^4He'$ system and the angle ($\theta$) between the measured photon and the 
missing momentum of the $e'^4He'$ system. The most relevant of these cuts are 
presented in Figure~\ref{fig:kin-cuts}, these are 3$\sigma$ cuts except for the 
missing energy that appears to be too large and for which we reduced the cut 
window to [-0.45,0.5] GeV. After these requirements, we have about 3200 events 
left, Figure \ref{fig:kin-coverage} presents their
kinematic distributions in ($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$).

@@

To interpret the DVCS, one has to keep in mind that this reaction is 
indistinguishable from the Bethe-Heitler (BH) process, where the final photon 
is emitted either from the incoming or the outgoing leptons. At leading twist 
and leading order, the deeply virtual photon production cross section is 
composed of a BH, a DVCS, and an interference terms. The amplitudes of the 
three terms can be approximated as a finite sum of Fourier harmonics as shown 
for the nucleon in \cite{Belitsky:2001ns} and for the spin-zero targets in 
\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on these calculations, the 
beam-spin asymmetry ($A_{LU}$) of a spin-zero hadron can then be expressed as:

\small
\begin{equation}
\begin{split}
A_{LU}(\phi) =~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
 \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( 
\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
\label{eq:A_LU-coh}
\end{split}
\end{equation}
\normalsize
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the $^4$He CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$. 
$\phi$ is the azimuthal angle between the ($e$,$e'$) and 
($\gamma^{*}$,$^4$He$'$) planes. The $\alpha_{i}$'s are $\phi$-dependent 
kinematical factors that depend on the nuclear form factor ($F_{A}(t)$) and the 
independent variables $Q^2$, $x_{B}$ and $t$. These factors are expressed as:
\small
\begin{eqnarray}
   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
C_{++}(1) cos(\phi) \right)\\
\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2}
\end{eqnarray}
\normalsize
Where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$ is the $^4$He mass, 
$\mathcal{P}_1(\phi)$ and $\mathcal {P}_2(\phi)$ are the Bethe-Heitler
propagators. The factors: $c_{0,1,2}^{BH}$, $c_0^{DVCS}$, $c_{0,1}^{INT}$ and
$s_1^{INT}$ are the Fourier coefficients of the BH, $S{++}(1)$, $C_{++}(0)$, 
and $C_{++}(1)$ are the Fourier harmonics in the leptonic tensor. The 
explicit expressions of these terms can be found in \cite{Belitsky:2008bz}. 
We see that using the $\sin(\phi)$ and $\cos(\phi)$ contributions, it is 
possible to extract 
$\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ from the beam spin
asymmetry.

@@

We display in figure \ref{fig:CFF_HA} our extraction of the $^4$He CFF 
$\mathcal{H}_A$ together with theoretical calculations from two models 
labeled: convolution, and off-shell models. In the convolution 
model \cite{Vadim_priv}, the nucleus is assumed to be composed of 
non-relativistic non-interacting nucleons, and these nucleons interact 
independently with the probe. The convolution/dual model is based on nucleon GPDs from 
the dual parametrization \cite{Guzey:2006xi}, the convolution/VGG uses nucleon GPDs  
from the VGG model, which is based on the double distributions ansatz 
\cite{DD_model}. The Off-shell model \cite{GonzalezHernandez:2012jv} relies on 
impulse approximation and uses advanced spectral function of the 
nuclei that accounts for all configurations of the final nuclear system and the 
binding effects between the nucleons.
[These need to be renamed on the figure, it does not make sense to call differently
models that are identical. We should also request the projections from Vadim
model: hep-ph/0509158. (Mohammad to Raphael, the projections shown in figure 5 
are for Carbon-12. Why would we added them?]

@@

\bibitem{Burkardt:2000za} 
  M.~Burkardt,
  Phys.\ Rev.\ D {\bf 62}, 071503 (2000)
  Erratum: Phys.\ Rev.\ D {\bf 66}, 119903 (2002)

\bibitem{Diehl:2002he} 
  M.~Diehl,
  Eur.\ Phys.\ J.\ C {\bf 25}, 223 (2002)
  Erratum: Eur.\ Phys.\ J.\ C {\bf 31}, 277 (2003)

@@

@@

\bibitem{Mecking:2003zu} 
   B.~A.~Mecking {\it et al.} [CLAS Collaboration],
   Nucl.\ Instrum.\ Meth.\ A {\bf 503}, 513 (2003).

%\bibitem{eg6_note}
%M. Hattawy {\it et al.} (CLAS-EG6 Working Group), CLAS internal analysis note, 
%2016.
